Minimizing post-shock forecasting error using disparate information

### 2020-06-12 manuscript/fig2.tex
Revisions to abstract, introduction, simulation, data analysis, and discussions.

% Created by tikzDevice version 0.12.3 on 2020-06-09 17:22:19
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 91.16) --
	(481.73, 86.58) --
	(476.44, 86.58) --
	(479.09, 91.16);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 87.98) -- (481.86, 87.98);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 85.20) -- (479.09, 90.75);
\definecolor{drawColor}{RGB}{238,99,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 86.20) -- (481.05, 90.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 90.12) -- (481.05, 86.20);
\definecolor{drawColor}{RGB}{238,130,238}
\definecolor{fillColor}{RGB}{238,130,238}

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 66.76,148.08) {$\hat{y}_{1, T_1^* + 1}^{1}$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 66.76,131.74) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm adj}$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 66.76,115.39) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm IVW}$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.10] at ( 66.76, 99.04) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm wadj}$};

\path[fill=fillColor] ( 53.02,151.88) circle (  1.96);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.02,138.59) --
	( 55.66,134.01) --
	( 50.37,134.01) --
	( 53.02,138.59);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.24,119.19) -- ( 55.79,119.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.02,116.42) -- ( 53.02,121.97);
\definecolor{drawColor}{RGB}{238,99,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.05,100.88) -- ( 54.98,104.81);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 51.05,104.81) -- ( 54.98,100.88);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,361.35);
\definecolor{drawColor}{gray}{0.30}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.32] at (266.05,346.76) {Conoco Phillips Stock Forecasting (2020--01--24 to 2020--03--09)};
\end{scope}
\end{tikzpicture}

>>>>

% Created by tikzDevice version 0.12.3 on 2020-06-11 18:44:46
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 91.25) --
	(481.73, 86.67) --
	(476.44, 86.67) --
	(479.09, 91.25);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 88.07) -- (481.86, 88.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 85.29) -- (479.09, 90.84);
\definecolor{drawColor}{RGB}{238,99,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 86.29) -- (481.05, 90.21);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 90.21) -- (481.05, 86.29);
\definecolor{drawColor}{RGB}{238,130,238}
\definecolor{fillColor}{RGB}{238,130,238}

@@

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.42] at ( 66.76,176.41) {$\hat{y}_{1, T_1^* + 1}^{1}$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.42] at ( 66.76,150.25) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm adj}$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.42] at ( 66.76,124.10) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm IVW}$};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.42] at ( 66.76, 97.94) {$\hat{y}_{1, T_1^* + 1}^{1} + \hat{\alpha}_{\rm wadj}$};

\path[fill=fillColor] ( 53.02,181.31) circle (  2.50);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.02,159.04) --
	( 56.38,153.21) --
	( 49.65,153.21) --
	( 53.02,159.04);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 49.48,129.00) -- ( 56.55,129.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.02,125.47) -- ( 53.02,132.53);
\definecolor{drawColor}{RGB}{238,99,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.52,100.35) -- ( 55.51,105.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.52,105.34) -- ( 55.51,100.35);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,361.35);
\definecolor{drawColor}{gray}{0.30}

@@

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.32] at (266.05,346.76) {Conoco Phillips Stock Forecasting (2020 January 24th to 2020 March 9th)};
\end{scope}
\end{tikzpicture}
